Research training portfolio

### 2012-12-18 Research training portfolio.tex
RTP: added pictures and bibliography

%Plaatje toevoegen

@@

\subsubsection{ErrorlistChecker (context-free)}
Martin Reynaert provided us with a large list of common typos and their corrections. This module, written by me, checks for every word in the input whether it's in the errorlist, and adds the correction when it is.

\subsubsection{LexiconChecker (context-free)}
Google provided us with an enormous list of word frequencies on the internet in 2008. The LexiconChecker checks for every word in the input whether there's a word on the frequencylist that is very similar to it, but much more frequent.

\subsubsection{RunonChecker (context-free)}
The RunonChecker also uses Google's list, but uses it to check if any spaces were forgotten in the input. This is done by looking whether splitting up long words produces two words which both are much more frequent that the original word.

\subsubsection{SplitChecker (context-free)}
The SplitChecker is the exact opposite of the RunonChecker: instead of looking whether any spaces are forgotten, it checks whether any spaces have to be added. This is done by looking whether each combination of two words produces a word which is much more frequent than the two original words.

\subsubsection{WOPRChecker (context-based)}
The WOPRChecker contacts WOPR, running on a server on localhost or elsewhere. It gives it the context of each word, but not the words themselves. If WOPR predicts another word with much certainty, this word is added as a correction.

\subsubsection{The ConfusibleCheckers (context-based)}
The ConfusibleCheckers work similar to the WOPRChecker, with the only difference that they are trained on one specific language problem, instead of on language in general. As I write this, there are fifteen active ConfusibleCheckers, all focussing on their own expertise: lose-loose, it's-its, you're-your, than-then, who-which-that, whether-weather, effect-affect, lie-lay, they're-their-there, don't-doesn't,to-too-two, advice-advise, any-some, less-fewer, practice-practise and chose-choose.
\\\indent
A ConfusibleChecker trained on the difference between 'then' and 'than' for example filters out these two words and their contexts, sends these contexts to a Timblserver running somewhere. This Timblserver then says which of the two it would predict on the basis of the context. If this prediction is different from the actual word and the server is very sure about this, the word is flagged as an error. Training new ConfusibleModules has been a large part of my internship.

\subsubsection{Fowlt as a web application}
%Picture reference
Fowlt can also (and, probably, will mostly) be used as a website. In this web variant, Fowlt works exactly as described above, but some extra mechanisms are built around to make sure it works and looks nice in the browser. The transition from a standalone application to a website is a two-step process, as is exemplified by figure... . Firstly, Fowlt is made available online webservice using the software CLAM. Among other things, CLAM adds the possibility to use Fowlt as a RESTful service. However, ordinary users don't want to send HTTP requests or read xml files when they want to texts corrected. This is solved in the second step, which is the Fowlt.net interface. In this interface, users can paste their texts, and see the mistakes flagged in red in these texts themselves. The interface even adds functionality to correct any errors. Behind the screens, the interface communicates of course with the CLAM webservice.
\\\indent
%Section reference
Most of the functionality described above was already working for Valkuil, and so only had to be adapted to English to be function within Fowlt. One feature that I created for Fowlt that Valkuil doesn't have (yet), is an error tolerance slider. With this slider, users can change on the fly how confident Fowlt has to be about an error before it displays it. The implementation of this slider was, however, not without problems. See section \ref{formulas} more information on that.

@@

% Voordelen Linux?

@@

% stat toevoegen

@@

@@

% TODO
% Eenduidige terminologie hanteren:  modulenamen
% Appendix

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=1\textwidth]{fowlt_chain.png}
\caption{Fowlt's architecture}
\label{fig:chain}
\end{figure}

@@

\subsubsection{Errorlist module (context-free)}
Martin Reynaert provided us with a large list of common typos and their corrections. This module, written by me, checks for every word in the input whether it's in the errorlist, and adds the correction when it is.

\subsubsection{Lexicon module (context-free)}
Google provided us with an enormous list of word frequencies on the internet in 2008. The LexiconChecker checks for every word in the input whether there's a word on the frequencylist that is very similar to it, but much more frequent.

\subsubsection{Runon module (context-free)}
The RunonChecker also uses Google's list, but uses it to check if any spaces were forgotten in the input. This is done by looking whether splitting up long words produces two words which both are much more frequent that the original word.

\subsubsection{Split module (context-free)}
The SplitChecker is the exact opposite of the RunonChecker: instead of looking whether any spaces are forgotten, it checks whether any spaces have to be added. This is done by looking whether each combination of two words produces a word which is much more frequent than the two original words.

\subsubsection{WOPR module(context-based)}
The WOPRChecker contacts WOPR, running on a server on localhost or elsewhere. It gives it the context of each word, but not the words themselves. If WOPR predicts another word with much certainty, this word is added as a correction.

\subsubsection{The Confusible modules (context-based)}
The ConfusibleCheckers work similar to the WOPRChecker, with the only difference that they are trained on one specific language problem, instead of on language in general. As I write this, there are fifteen active ConfusibleCheckers, all focussing on their own expertise: lose-loose, it's-its, you're-your, than-then, who-which-that, whether-weather, effect-affect, lie-lay, they're-their-there, don't-doesn't,to-too-two, advice-advise, any-some, less-fewer, practice-practise and chose-choose.
\\\indent
A ConfusibleChecker trained on the difference between 'then' and 'than' for example filters out these two words and their contexts, sends these contexts to a Timblserver running somewhere. This Timblserver then says which of the two it would predict on the basis of the context. If this prediction is different from the actual word and the server is very sure about this, the word is flagged as an error. Training new ConfusibleModules has been a large part of my internship.

\subsubsection{Fowlt as a web application}
Fowlt can also (and, probably, will mostly) be used as a website. In this web variant, Fowlt works exactly as described above, but some extra mechanisms are built around to make sure it works and looks nice in the browser. The transition from a standalone application to a website is a two-step process, as is exemplified by Figure \ref{fig:chain}. Firstly, Fowlt is made available online webservice using the software CLAM. Among other things, CLAM adds the possibility to use Fowlt as a RESTful service. However, ordinary users don't want to send HTTP requests or read xml files when they want to texts corrected. This is solved in the second step, which is the Fowlt.net interface. In this interface, users can paste their texts, and see the mistakes flagged in red in these texts themselves. The interface even adds functionality to correct any errors. Behind the screens, the interface communicates of course with the CLAM webservice.
\\\indent
%Section reference
Most of the functionality described above was already working for Valkuil, and so only had to be adapted to English to be function within Fowlt. One feature that I created for Fowlt that Valkuil doesn't have (yet), is an error tolerance slider. With this slider, users can change on the fly how confident Fowlt has to be about an error before it displays it. The implementation of this slider was, however, not without problems. See section \ref{formulas} more information on that.

@@

@@

@@

\subsection{Advice versus advice corrector}

\begin{table}[H] \footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
&&P&N\\
\hline
balanced&Y&0&0\\
&N&0&0\\
\hline
\hline
unbalanced&Y&0&0\\
&N&0&0\\
\hline
\end{tabular}
\caption{The confusion matrices for the corrector for the \emph{advice} versus \emph{advise}, trained on both a balanced and an inbalanced data set.}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_adviceadvise.png}
\caption{The accuracies of corrector for the \emph{advice} versus \emph{advise}, trained on both a balanced and an inbalanced data set.}
\end{figure}

\subsection{Lose versus loose corrector}

\begin{table}[H] \footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
&&P&N\\
\hline
balanced&Y&0&0\\
&N&0&0\\
\hline
\hline
unbalanced&Y&0&0\\
&N&0&0\\
\hline
\end{tabular}
\caption{The confusion matrices for the corrector for the \emph{lose} versus \emph{loose}, trained on both a balanced and an inbalanced data set.}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_loseloose.png}
\caption{The accuracies of corrector for the \emph{lose} versus \emph{loose}, trained on both a balanced and an inbalanced data set.}
\end{figure}

\subsection{Practice versus practise corrector}

\begin{table}[H] \footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
&&P&N\\
\hline
balanced&Y&0&0\\
&N&0&0\\
\hline
\hline
unbalanced&Y&0&0\\
&N&0&0\\
\hline
\end{tabular}
\caption{The confusion matrices for the corrector for the \emph{practice} versus \emph{practise}, trained on both a balanced and an inbalanced data set.}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_practicepractise.png}
\caption{The accuracies of corrector for the \emph{practice} versus \emph{practise}, trained on both a balanced and an inbalanced data set.}
\end{figure}

\subsection{Than versus then corrector}

\begin{table}[H] \footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
&&P&N\\
\hline
balanced&Y&0&0\\
&N&0&0\\
\hline
\hline
unbalanced&Y&0&0\\
&N&0&0\\
\hline
\end{tabular}
\caption{The confusion matrices for the corrector for the \emph{than} versus \emph{then}, trained on both a balanced and an inbalanced data set.}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_thanthen.png}
\caption{The accuracies of corrector for the \emph{than} versus \emph{then}, trained on both a balanced and an inbalanced data set.}
\end{figure}

\subsection{Weather versus whether corrector}

\begin{table}[H] \footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
&&P&N\\
\hline
balanced&Y&0&0\\
&N&0&0\\
\hline
\hline
unbalanced&Y&0&0\\
&N&0&0\\
\hline
\end{tabular}
\caption{The confusion matrices for the corrector for the \emph{weather} versus \emph{whether}, trained on both a balanced and an inbalanced data set.}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_weatherwhether.png}
\caption{The accuracies of corrector for the \emph{weather} versus \emph{whether}, trained on both a balanced and an inbalanced data set.}
\end{figure}

\subsection{You're versus your corrector}

\begin{table}[H] \footnotesize
\centering
\begin{tabular}{|c|c|c|c|}
\hline
&&P&N\\
\hline
balanced&Y&0&0\\
&N&0&0\\
\hline
\hline
unbalanced&Y&0&0\\
&N&0&0\\
\hline
\end{tabular}
\caption{The confusion matrices for the corrector for the \emph{you're} versus \emph{your}, trained on both a balanced and an inbalanced data set.}
\end{table}

\begin{figure}[H]
\centering
\includegraphics[width=0.8\textwidth]{accuracy_you'reyour.png}
\caption{The accuracies of corrector for the \emph{you're} versus \emph{your}, trained on both a balanced and an inbalanced data set.}
\end{figure}

@@
